---
title: "Antibiotics Transporters"
author: "Lachlan Munro"
date: "24/3/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load all libraries. 

```{r}
#Load libraries
library(data.table)
library(dplyr)
library(platetools)
library(growthcurver)
library(openxlsx)
library(reshape2)
library(ggplot2)
library(stringr)
library(plotly)
library(htmlwidgets)
library(ggpointdensity)
library(d3heatmap)
library(tidyr)
library(Hmisc)


```


Functions to covert g Values to OD. This is the same formula used when converting within the Growth Profiler software however when using the older software version the conversion isn't available. 

```{r}

od_LB<- function(x) {
0.0158*(x-26.717)^0.9854
}

```

Load plates data with strain information and generate a data frame. 
This is hard-coded for positions of each strain from the "Plates.csv" file. 

```{r}


plates <- read.csv("Plates.csv", sep=";", header=TRUE)
plates.df <- data.frame(Well = rep(num_to_well(c(1:96)),5), strain = as.vector(t(plates[,c(2:13)])), Plate = sort(rep(c(1:5), 96)))

```

Functions to read from csv and convert G_Values to OD, to generate growth data using Growthcurver 
and to add strain information.


```{r}

#Fix when growthprofiler output formatting changed 
correct_commas <- function(df){
  data.frame(lapply(df, function(x){as.numeric(chartr(",", ".", x))}))
}


#Take a single CSV file of raw G values or OD values (one plate) and return a dataframe of OD values.
generate_table <- function(filename){
  df <- fread(filename, header=TRUE, skip="Time (min)")
  d <- correct_commas(df)
  colnames(d)[1] <- "time"
  #Convert to OD if not already done in GPViewer software
  d_od <- d
  if(!grepl("OD", filename)){
        d_od <- as.data.frame(apply(d[,2:97], 2, od_LB))
        }
  
  d_od$time <- seq(0, by=1/3, length.out=nrow(d_od))
  d_od[is.na(d_od)] <- 0
  d_od <- subset(d_od, select = c(time, A1:H12))
  #Select just the first approx. 24 hours to account for differences in run times
  d_od <- d_od[c(1:70), ]
  return(d_od)
}


#Convert dataframe to growth parameters
generate_gpCurves <- function(df){
  df_1 <- df[2:97]
  gc_plate <- SummarizeGrowthByPlate(df)
  #add column which contains Max OD 
  maxes <- apply(df_1, 2, FUN=max)
  gc_plate["max"] <- maxes
  gc_plate$well <- num_to_well(1:96)
  gc_plate$tdt <- log(2)/gc_plate$r
  #Correct for very low growth conditions which give artificially high R. Will need to correct for OD
  gc_plate<- mutate(gc_plate, adj.r = ifelse(r>2 & auc_e < 5, 0, r))
  return(gc_plate)
}

#Add strain information to dataframe based on plate position
add_strains <- function(df, n){
  x <- ifelse(n>5, n-5, n )
  strains = as.character(plates.df[plates.df$Plate==x,]$strain)
  df["Strains"] <- strains
  df["Position"] <- rep(n, 96)
  return(df)
 }


generate_data <- function(file){
  pos = as.numeric(substr(str_extract(file,  "MTP\\d+"), 4, 6))
  df <- generate_table(file)
  df.gp <- generate_gpCurves(df)
  df.gp.strains <- add_strains(df.gp, pos)
  return(df.gp.strains)
}



compoundFolder <- function(compound){
  folder = paste("ResultCSVs", compound, sep="_")
  return(folder)
}

#makes a summary dataframe for a full run
make_compound_df <- function(compound){
  folder <- compoundFolder(compound)
  files <- list.files(paste(folder, "/", sep=""))
  #Check if OD has already been calculated, otherwise take raw values. 
  gvalueFiles <- grep("MTP[0123456789]+_OD.csv",files,value=TRUE)
  if(length(gvalueFiles) == 0){
    gvalueFiles <-  grep("MTP[0123456789]+_GValue.csv", files, value = TRUE)
  }
  gvalueFiles <- paste(folder, gvalueFiles, sep="/")
  d <- lapply(gvalueFiles, generate_data)
  df <- bind_rows(d)
return(df)
}

#Returns the mean if both values are numbers, else the single value if one is 0
mean_or_only <- function(x){
  x[is.na(x)] <- 0
  minx <- min(x)
  maxx <- max(x)
  ifelse(maxx > 100*minx, y <- max(x), y<- mean(x))
  return(y)
}

#makes a summary dataframe with all neccesary values. 

make_Summary_df <- function(df){
  summ_df <- group_by(df, Strains)
  summary_df <- summarise(summ_df, mean_max_od = mean_or_only(max), min_max_od = min(max), max_max_od=max(max), mean_rate = mean_or_only(adj.r), min_rate= min(adj.r), max_rate=max(adj.r), t_mid_mean = mean_or_only(t_mid), t_mid_max = max(t_mid), t_mid_mid = min(t_mid), min_auc = min(auc_e), max_auc = max(auc_e), mean_auc = mean_or_only(auc_e))
}

make_Summary_df_from_compound <- function(compound){
  df <- make_compound_df(compound)
  df <- mutate_all(df, ~replace_na(.,0))
  summarydf <- make_Summary_df(df)
  summarydf[,"Antibiotic"] <- compound
  return(summarydf)
}

```

Generate WT Values

```{r}

raw_lbDF <- make_compound_df("LB")

wt_rawLB <- raw_lbDF[raw_lbDF$Strains == "wt",]

mean_rate.wt_lb <- mean(wt_rawLB$adj.r[wt_rawLB$adj.r !=0])

mean_AUC.wt_lb <- mean(wt_rawLB$auc_e[wt_rawLB$auc_e != 0])



```



Generate baseline growth rates using LB data and make histograms. 

```{r}
lb_df <- make_Summary_df_from_compound("LB")


#Calculate WT growth rate 



lb_hist_rate <- ggplot(data=lb_df, aes(max_rate)) + geom_histogram(color = "lightblue", fill="lightblue", bins=75) +
    theme_minimal() + 
    geom_vline(xintercept = mean_rate.wt_lb)+ #WT Rate calculated and hardcoded
    theme(axis.text = element_text(size=12), panel.border = element_rect(colour = "black", fill=NA, size=2), legend.text = element_text(size=12))+
    xlab("Growth Rate h"^"-1") + ylab("Strain Count")+
    scale_x_continuous(breaks=c(0.2, 0.4,0.6, 0.8, 1, 1.2, 1.4, 1.6, 1.8)) + xlim(0, 1.5) + theme(axis.text = element_text(size=16), axis.title = element_text(size=18))

lb_hist_auc <- ggplot(data=lb_df, aes(mean_auc)) + geom_histogram(color = "lightblue", fill="lightblue", bins=75) + 
    theme_minimal() + 
    geom_vline(xintercept = mean_AUC.wt_lb)+ #WT AUC Calculated and hardcoded.
    theme(axis.text = element_text(size=12), panel.border = element_rect(colour = "black", fill=NA, size=2), legend.text = element_text(size=12))+
    xlab("AUC") + ylab("Strain Count")+ theme(axis.text = element_text(size=16), axis.title = element_text(size=18))

lb_hist_auc + xlim(0, 35)
lb_hist_rate

```


```{r}
filt.lbdf <- lb_df[!lb_df$min_max_od==0 & lb_df$max_max_od > 0,]

ggplot(data = filt.lbdf, aes(x=min_rate, y=max_rate)) + geom_point() + theme_bw() + theme(axis.text = element_text(size=12), panel.border = element_rect(colour = "black", fill=NA, size=2), legend.text = element_text(size=12))+
    xlab("Replicate 2 ") + ylab("Replicate 1")+ theme(axis.text = element_text(size=16), axis.title = element_text(size=18))

ggplot(data = filt.lbdf, aes(x=min_auc, y=max_auc)) + geom_point() + theme_bw() + theme(axis.text = element_text(size=12), panel.border = element_rect(colour = "black", fill=NA, size=2), legend.text = element_text(size=12))+
    xlab("Replicate 2 ") + ylab("Replicate 1")+ theme(axis.text = element_text(size=16), axis.title = element_text(size=18))


```



```{r}
remove_outliers <- function(x){
  x <- x[x!=0]
  stddev <- sd(x)
  m <- mean(x)
  cutoff <- m + 2*stddev
  x <- x[x<cutoff]
}
```





Function to generate masters figures list and data from compound: 

```{r}

make_figs_compound <- function(compound){
  media <- lb_df
  df <- make_compound_df(compound)
  #Exclude wt values with no growth
  wt_vals <- df[which(df$Strains == "wt"),]
  wt_vals <- wt_vals[wt_vals$adj.r > 0 & wt_vals$note != "questionable fit (k < n0)" & wt_vals$note != "cannot fit data",]
  #Exclude outliers
  wt_mean_r <- as.numeric(mean(remove_outliers(wt_vals$adj.r)))
  wt_mean_r <- wt_mean_r/mean_rate.wt_lb                       
  wt_sd_r <- as.numeric(sd((wt_vals$adj.r))/media[(which(media$Strains=="wt")), "mean_rate"])

  wt_mean_maxOD <- as.numeric(mean(wt_vals$max)/media[(which(media$Strains=="wt")), "mean_max_od"])
  
  wt_mean_lag <- as.numeric(mean(wt_vals$t_mid)/media[(which(media$Strains=="wt")), "t_mid_mean"])
  
  
  summ_df_orig <- make_Summary_df(df)
  
  summ_df_media <- merge(summ_df_orig, media, by.x="Strains", by.y="Strains")
  names(summ_df_media) <- str_replace(names(summ_df_media), "\\.x", "_compound")
  names(summ_df_media) <- str_replace(names(summ_df_media), "\\.y", "_media")
  
  summ_df_norm <- mutate(summ_df_media, mean_rate_norm = mean_rate_compound/mean_rate_media,
                         mean_maxod_norm = mean_max_od_compound/mean_max_od_media,
                         mean_t_mid_norm = t_mid_mean_compound/t_mid_mean_media, 
                         mean_auc_norm = mean_auc_compound/mean_auc_media)
  
  summ_df_norm$Antibiotic <- compound
  
  # #Filter out missed Innoculations
  f <- which(summ_df_norm$min_auc_compound < 1 & summ_df_norm$max_auc_compound > 5)
  # summ_df_norm <- summ_df_norm[-f,]
  
  #Rate Histogram
  
  hst_rate <- ggplot(data = summ_df_norm, aes(mean_rate_norm))+
    geom_histogram(color = "lightblue", fill="lightblue", bins=75) + 
    theme_minimal() + 
    geom_vline(xintercept = wt_mean_r)+
    theme(axis.text = element_text(size=12),panel.border = element_rect(colour = "black", fill=NA, size=2), legend.text = element_text(size=12))+
    xlab("Growth Rate Ratio ") + ylab("Strain Count")+
    scale_x_continuous(breaks=c(0.2, 0.4,0.6, 0.8, 1, 1.2, 1.4, 1.6, 1.8)) + xlim(0, 1.5)+theme(axis.text = element_text(size=16),panel.border = element_rect(colour = "black", fill=NA, size=3), legend.text = element_text(size=16), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.title = element_text(size=18))

  #max_od_histogram
hst_maxOD <- ggplot(data = summ_df_norm, aes(mean_maxod_norm))+
    geom_histogram(color = "lightblue", fill="lightblue", bins=75) + 
    theme_minimal() + 
    geom_vline(xintercept = wt_mean_maxOD)+
    theme(axis.text = element_text(size=12),panel.border = element_rect(colour = "black", fill=NA, size=2), legend.text = element_text(size=12))+
    xlab("Max OD600 Ratio ") + ylab("Strain Count")+
    scale_x_continuous(breaks=c(0.2, 0.4,0.6, 0.8, 1, 1.2, 1.4, 1.6, 1.8)) + xlim(0, 1.5)

#hst_auc
hst_auc <- ggplot(data = summ_df_norm, aes(mean_auc_norm))+
    geom_histogram(color = "lightblue", fill="lightblue", bins=75) + 
    theme_minimal() + 
    geom_vline(xintercept = wt_mean_maxOD)+
    theme(axis.text = element_text(size=16),panel.border = element_rect(colour = "black", fill=NA, size=3), legend.text = element_text(size=16), panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())+
    xlab("AUC Rate") + ylab("Strain Count")+theme(axis.text = element_text(size=16),panel.border = element_rect(colour = "black", fill=NA, size=3), legend.text = element_text(size=16), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.title = element_text(size=18))

hst_lag <-   ggplot(data = summ_df_norm, aes(mean_t_mid_norm))+
    geom_histogram(color = "lightblue", fill="lightblue", bins=75) + 
    theme_minimal() + 
    geom_vline(xintercept = wt_mean_lag)+
    theme(axis.text = element_text(size=12),panel.border = element_rect(colour = "black", fill=NA, size=2), legend.text = element_text(size=12))+
    xlab("Lag Ratio") + ylab("Strain Count")+
    scale_x_continuous(breaks=c(0.2, 0.4,0.6, 0.8, 1, 1.2, 1.4, 1.6, 1.8))

auc_cor <- ggplot(data=summ_df_norm, aes(min_auc_compound, max_auc_compound)) + geom_point() + theme_minimal()

    
  return(list(rate = hst_rate, maxod = hst_maxOD, auc = hst_auc, lag = hst_lag, dataFrame = summ_df_norm, Correlation = auc_cor, Filtered = f, WT = c(wt_mean_r, wt_sd_r)))
}




```

Generate master list of figures from all compounds 

```{r}

azithromycin <- make_figs_compound("Azithromycin")

lb <- make_figs_compound("LB")

ornidazole <- make_figs_compound("Ornidazole")

cefoperazone <- make_figs_compound("Cefoperazone")

chloramphenicol <- make_figs_compound("Chloramphenicol")

meropenem <- make_figs_compound("Meropenem")

gentamycin <- make_figs_compound("Gentamycin")

zidovudine <- make_figs_compound("Zidovudine")

flum <- make_figs_compound("Flumequine2")

dcycloserine <- make_figs_compound("D-Cycloserine")

#Redo of cefiderocool run due to very odd results 
cefiderocol2 <- make_figs_compound("Cefiderocol2")
cefiderocol <- make_figs_compound("Cefiderocol")


ofloxacin <- make_figs_compound("Ofloxacin")

streptomycin <- make_figs_compound("Streptomycin")

rifampicin <- make_figs_compound("Rifampicin")

levofloxacin <- make_figs_compound("Levofloxacin")

paraquat <- make_figs_compound("ParaquatLB")

trimethoprim <- make_figs_compound("Trimethoprim")

phosphomycin <- make_figs_compound("Phosphomycin")

ceftriaxone <- make_figs_compound("Ceftriaxone")

```



Making rank Figures
```{r}

checkYgene <- function(x){
  y <- ifelse(startsWith(x, "y"), "yGene", "Not yGene")
}

make_rank_rate_fig <- function(df){
  df <- df[order(df$mean_auc_compound),]
  df <- mutate(df, ygene = checkYgene(Strains))
  df$ygene[which(df$Strains == "wt")] <- "WT"
  
  p <- ggplot(data = df, aes(x=c(1:nrow(df)), y=mean_auc_compound)) + 
    geom_point(aes(color = ygene), size=2, shape=4) + theme_bw() + ylab("Mean AUC") + xlab("Knockout List Ordered by Mean AUC") + theme(axis.title = element_text(size=18),
          axis.text = element_text(size=16),
          axis.text.x = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          legend.position = "none",
          panel.border = element_rect(colour = "black", size = 4)) + ylim(0, 35)
  
}

                    
```




```{r}
rank_figs <- lapply(list(lb$dataFrame, 
                                       ornidazole$dataFrame, 
                                       cefiderocol2$dataFrame, 
                                       cefoperazone$dataFrame, 
                                       meropenem$dataFrame, 
                                       gentamycin$dataFrame, 
                                       zidovudine$dataFrame, 
                                       flum$dataFrame, 
                                       dcycloserine$dataFrame, 
                                       azithromycin$dataFrame, 
                                       ofloxacin$dataFrame, 
                                       streptomycin$dataFrame, 
                                       rifampicin$dataFrame, 
                                       paraquat$dataFrame, 
                                       levofloxacin$dataFrame, 
                                       phosphomycin$dataFrame,
                                       trimethoprim$dataFrame,
                                       ceftriaxone$dataFrame), 
                    make_rank_rate_fig)

rank_figs[[1]]
rank_figs[[17]]
rank_figs[[4]]
rank_figs[[14]]
     
```




```{r}
antibiotics_vect <- c("LB", "Azithromycin", "Cefoperazone", "Ceftriaxone", "Cifoderocol2", "D-Cycloserine", "Flumequine2", "Gentamycin", "Levofloxacin",  "Meropenem" ,"Ofloxacin","Ornidazole","ParaquatLB",   "Phosphomycin","Rifampicin","Streptomycin","Trimethoprim","Zidovudine")


```

Generation of master dataframe with all data and scatterplot to highlight correlation between strains. 

```{r}
antibioticsDF <- do.call("rbind", list(lb$dataFrame, 
                                       ornidazole$dataFrame, 
                                       cefiderocol2$dataFrame, 
                                       cefoperazone$dataFrame, 
                                       meropenem$dataFrame, 
                                       gentamycin$dataFrame, 
                                       zidovudine$dataFrame, 
                                       flum$dataFrame, 
                                       dcycloserine$dataFrame, 
                                       azithromycin$dataFrame, 
                                       ofloxacin$dataFrame, 
                                       streptomycin$dataFrame, 
                                       rifampicin$dataFrame, 
                                       paraquat$dataFrame, 
                                       levofloxacin$dataFrame, 
                                       phosphomycin$dataFrame,
                                       trimethoprim$dataFrame,
                                       ceftriaxone$dataFrame,
                                       chloramphenicol$dataFrame))


antibioticsDF$Antibiotic <- as.factor(antibioticsDF$Antibiotic)
antibioticsDF$Antibiotic <- factor(antibioticsDF$Antibiotic, levels = c("LB", "Azithromycin", "Cefoperazone", "Ceftriaxone", "Cefiderocol2", "D-Cycloserine", "Flumequine2", "Gentamycin", "Levofloxacin",  "Meropenem" ,"Ofloxacin","Ornidazole","ParaquatLB",   "Phosphomycin","Rifampicin","Streptomycin","Trimethoprim","Zidovudine", "Chloramphenicol"))

levels(antibioticsDF$Antibiotic) <- c("LB", "Azithromycin", "Cefoperazone", "Ceftriaxone","Chloramphenicol", "Cifoderocol", "D-Cycloserine", "Flumequine", "Gentamycin", "Levofloxacin",  "Meropenem" ,"Ofloxacin","Ornidazole","Paraquat",   "Phosphomycin","Rifampicin","Streptomycin","Trimethoprim","Zidovudine")

g <- ggplot(data=antibioticsDF, aes(Antibiotic, mean_auc_compound)) + geom_boxplot() +theme_bw() + 
    theme(axis.text.x = element_text(angle = 90), 
        axis.title = element_text(size=18),
          axis.text = element_text(size=16),
        axis.title.x = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          legend.position = "none",
          panel.border = element_rect(colour = "black", size = 3)) + ylim(0, 40) + ylab("Mean AUC")
  

g

```




Functions to generate time course plots:

```{r}
generate_timecourse <- function(file){
  pos = as.numeric(substr(str_extract(file,  "MTP\\d+"), 4, 6))
  x <- ifelse(pos>5, pos-5, pos )
  df <- generate_table(file)
  return(df)
}

generate_timecoures_compound <- function(compound){
  folder <- compoundFolder(compound)
  files <- list.files(paste(folder, "/", sep=""))

  gvalueFiles <- grep("MTP[0123456789]+_OD.csv",files,value=TRUE)
  if(length(gvalueFiles) == 0){
    gvalueFiles <-  grep("MTP[0123456789]+_GValue.csv", files, value = TRUE)
  }
  gvalueFiles <- paste(folder, gvalueFiles, sep="/")
  d <- lapply(gvalueFiles, generate_timecourse)
  df_1 <- Reduce(function(x, y) merge(x, y, by="time"), d)
}


extract_indices <- function(df, strain){
  # add one to account for time column in time course data frame
  #k < 50 is to account for weird wells that can be fit but don't actually grow
    inds <- which(df$Strains == strain & df$note != "questionable fit (k < n0)"& df$note != "cannot fit data" )+1
}


make_strain_df<- function(compound, strain){
  df <- make_compound_df(compound)
  tc <- generate_timecoures_compound(compound)
  wt_inds <- extract_indices(df, "wt")
  strain_inds <- which(df$Strains == strain) +1
  
  wt <- tc[,wt_inds]
  wtMean <- apply(wt, 1, mean)
  wtSD <- apply(wt, 1, function(x) sd(x)/sqrt(length(wt_inds)))
  
  strain <- tc[,strain_inds]
  strain1 <- strain[,1]
  strain2 <- strain[,2]
  
  df <- data.frame(time = tc$time, wtMean, wtSD, strain1, strain2)
  df$MeanStrain <- rowMeans(df[,c("strain1", "strain2")])
  df
}



plot_strain <- function(df, strain, compound){
  g <- ggplot(data=df, aes(x=time)) + geom_line(aes(y=wtMean), color = "black", size=2.5)+
    geom_ribbon(aes(ymin=wtMean - wtSD, ymax=wtMean + wtSD), alpha = 0.2, fill = "grey")+
    geom_line(aes(y=strain1), color = "red", size = 2) +
    geom_line(aes(y=strain2), color = "red", size=2) + 
    theme_minimal() + 
    labs(x ="Time (hours)" , y = "OD600")+
    ggtitle(paste("WT (black) vs ", strain, "(red) in ", compound)) + 
    xlim(c(0, 30))
    
  g
}

plot_strain_publication <- function(df){
  g <- ggplot(data=df, aes(x=time)) + geom_point(aes(y=wtMean), color = "black", size=2.5)+
    geom_line(aes(y=wtMean), color = "black", size=0.5)+
    geom_ribbon(aes(ymin=wtMean - wtSD, ymax=wtMean + wtSD), alpha = 0.2, fill = "grey")+
    geom_point(aes(y=MeanStrain), color = "red", size = 2) +
    geom_line(aes(y=MeanStrain), color = "red", size=0.5)+
    #geom_point(aes(y=strain2), color = "red", size=2) + 
    #geom_line(aes(y=strain2), color = "red", size=0.5)+
    theme_bw() + 
    labs(x ="Time (hours)" , y = "OD600")+
    theme(axis.title = element_text(size=18),
          axis.text = element_text(size=16),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_rect(colour = "black", size = 4))
}

make_plot_publication <- function(compound, strain){
  df <- make_strain_df(compound, strain)
  p <- plot_strain_publication(df)
  summaryWT <- SummarizeGrowth(df$time, df$wtMean)
  sumaryStrain <- SummarizeGrowth(df$time, df$MeanStrain)
  list(p, summaryWT, sumaryStrain)
}

make_plot <- function(compound, strain){
  df <- make_strain_df(compound, strain)
  p <- plot_strain(df, strain = strain, compound = compound)

}

```






Code to extract sorted DF
```{r}
get_sorted_df <- function(figs_list){
  df <- figs_list[[5]]
  df <- df[order(df$mean_auc_norm),]
}


write_excel_table_low <- function(figs_list){
  df <- get_sorted_df(figs_list)
  compound <- df[1, 26]
  df <- df[,c(1, 2, 5, 13, 27,28, 30)]
  
  names(df) <- c("Strain", "MaxOD", "Rate", "AUC", "Normalized MaxOD", "Normalized Rate", "Normalized AUC")
  b <- which(df$Strain == "BLANK")
  df <- df[-b,]
  


}


l <- lapply(list(lb, azithromycin, cefoperazone,ceftriaxone, cefiderocol2,  chloramphenicol,dcycloserine, flum, gentamycin, levofloxacin, meropenem, ofloxacin, ornidazole, paraquat, phosphomycin, rifampicin, streptomycin, trimethoprim, zidovudine), write_excel_table_low)

antibiotics_vect <- c("LB", "Azithromycin", "Cefoperazone", "Ceftriaxone", "Cifoderocol", "Chloramphenicol", "D-Cycloserine", "Flumequine", "Gentamycin", "Levofloxacin",  "Meropenem" ,"Ofloxacin","Ornidazole","Paraquat",   "Phosphomycin","Rifampicin","Streptomycin","Trimethoprim","Zidovudine")


names(l) <- antibiotics_vect

write.xlsx(l, "Supplementary.xlsx")



```


```{r}
acrBlist <- lapply(c("LB", "Azithromycin", "Cefoperazone", "Ceftriaxone", "Cefiderocol2", "D-Cycloserine", "Flumequine2", "Gentamycin", "Levofloxacin",  "Meropenem" ,"Ofloxacin","Ornidazole","ParaquatLB",   "Phosphomycin","Rifampicin","Streptomycin","Trimethoprim","Zidovudine", "Chloramphenicol"), make_plot_publication, strain = "acrB")


acrBlist[[19]][[1]]

```


Ornidazole histograms

```{r}
ornidazole[[1]]
ornidazole[[3]]
```


Ornidazole figure generation: 

```{r}
ornidazole_sorted <- get_sorted_df(ornidazole)

tail(ornidazole_sorted)

head(ornidazole_sorted[,c(1, 27, 30)], 20)

ybhR <- make_plot_publication("Ornidazole", "ybhR")
argO <- make_plot_publication("Ornidazole", "argO")
cysW <- make_plot_publication("Ornidazole", "cysW")
acrB <- make_plot_publication("Ornidazole", "acrB")
dham <- make_plot_publication("Ornidazole", "dhaM")
ydjE <- make_plot_publication("Ornidazole", "ydjE")

narU <- make_plot_publication("Ornidazole", "narU")

ygaH <- make_plot_publication("Ornidazole", "ygaH")


```

Meropenem figure generation: 

```{r, warning=FALSE}
meropenem_sorted <- get_sorted_df(meropenem)

tail(meropenem_sorted[,c(1, 13)])

mobd <- make_plot_publication("ParaquatLB", "yifK")

```


Azithromycin figure generation: 

```{r}

azizSorted <- get_sorted_df(azithromycin)
head(azizSorted[,c(1, 11, 12,13, 30)], 10)


betT <- make_plot_publication("Azithromycin", "betT")
tolR <- make_plot_publication("Azithromycin", "tolR")
tolQ <- make_plot_publication("Azithromycin", "tolQ")
tyrP <- make_plot_publication("Azithromycin", "tyrP")
yiaM <- make_plot_publication("Azithromycin", "yiaM")
yraQ <- make_plot_publication("Azithromycin", "yraQ")
ydhW <- make_plot_publication("Azithromycin", "yhdW")
ydfJ <- make_plot_publication("Azithromycin", "ydfJ")
kgtP <- make_plot_publication("Azithromycin", "kgtP")

azizSorted

```
Paraquat


```{r, warning=FALSE}
paraquatsorted <- get_sorted_df(paraquat)

head(paraquatsorted[,c(1, 11, 12, 13)])

para_ydcz <- make_plot_publication("ParaquatLB", "ydcZ")
para_aroP <- make_plot_publication("ParaquatLB", "aroP")
para_acrB <- make_plot_publication("ParaquatLB", "acrB")
para_potH <- make_plot_publication("ParaquatLB", "potH")
para_yfeO <- make_plot_publication("ParaquatLB", "potH")

para_cusa <- make_plot_publication("ParaquatLB", "cusA")
para_fief <- make_plot_publication("ParaquatLB", "fieF")

```





```{r}
extractRate <- function(df){
  r <- df$mean_rate_norm 
}

extract_auc <- function(df){
  r <- df$mean_auc_compound
}


rateDF <- data.frame(do.call("cbind", lapply(list(lb$dataFrame, 
                                       ornidazole$dataFrame, 
                                       cefiderocol2$dataFrame, 
                                       cefoperazone$dataFrame, 
                                       meropenem$dataFrame, 
                                       gentamycin$dataFrame, 
                                       zidovudine$dataFrame, 
                                       flum$dataFrame, 
                                       dcycloserine$dataFrame, 
                                       azithromycin$dataFrame, 
                                       ofloxacin$dataFrame, 
                                       streptomycin$dataFrame, 
                                       rifampicin$dataFrame, 
                                       paraquat$dataFrame, 
                                       levofloxacin$dataFrame, 
                                       phosphomycin$dataFrame,
                                       trimethoprim$dataFrame,
                                       ceftriaxone$dataFrame), extractRate)))

aucDF <- data.frame(do.call("cbind", lapply(list(lb$dataFrame, 
                                       ornidazole$dataFrame, 
                                       cefiderocol2$dataFrame, 
                                       cefoperazone$dataFrame, 
                                       meropenem$dataFrame, 
                                       gentamycin$dataFrame, 
                                       zidovudine$dataFrame, 
                                       flum$dataFrame, 
                                       dcycloserine$dataFrame, 
                                       azithromycin$dataFrame, 
                                       ofloxacin$dataFrame, 
                                       streptomycin$dataFrame, 
                                       rifampicin$dataFrame, 
                                       paraquat$dataFrame, 
                                       levofloxacin$dataFrame, 
                                       phosphomycin$dataFrame,
                                       trimethoprim$dataFrame,
                                       ceftriaxone$dataFrame), extract_auc)))


rownames(rateDF) <- lb$dataFrame$Strains

names(aucDF) <- c("LB", "Azithromycin", "Cefoperazone", "Ceftriaxone", "Cifoderocol2", "D-Cycloserine", "Flumequine2", "Gentamycin", "Levofloxacin",  "Meropenem" ,"Ofloxacin","Ornidazole","ParaquatLB",   "Phosphomycin","Rifampicin","Streptomycin","Trimethoprim","Zidovudine")

ratedf.clean <- apply(rateDF, MARGIN = 1, function(x){ifelse(x > 10, 0, x)})

ratedf.norm <- scale(t(ratedf.clean), center = TRUE)

rownames(aucDF) <- lb$dataFrame$Strains



scal.auc.df <- scale(aucDF)

correlation <- cor(t(scal.auc.df))
correlation.pvalue <- rcorr(t(scal.auc.df))$P


hm <- d3heatmap(correlation, height = 1000, width = 1000)

saveWidget(hm, "Heatmap.html")

```


Code to generate histogram of pvalues 


```{r}
df <- data.frame(cor = c(correlation), p = c(correlation.pvalue))

ggplot(data = df, aes(x=cor)) + geom_histogram(bins=100)

ggplot(data = df, aes(x=p)) + geom_histogram(color = "lightblue", fill="lightblue", bins=300) + theme_bw()+ ylab("Count") + xlab("P- Value") + theme(axis.title = element_text(size=18),
          axis.text = element_text(size=16),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          legend.position = "none",
          panel.border = element_rect(colour = "black", size = 2))


pvalhist <- ggplot(data = df, aes(x=p)) + geom_histogram(color = "lightblue", fill="lightblue", bins=300) + theme_bw()+ ylab("Count") + xlab("P- Value") + theme(axis.title = element_text(size=18),
          axis.text = element_text(size=16),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          legend.position = "none",
          panel.border = element_rect(colour = "black", size = 2))



```


```{r}

sig_values <- which(correlation.pvalue < 0.05/(447*446), arr.ind = TRUE)
sig_inds <- which(correlation.pvalue < 0.05/(447*446))

rows <- as.vector(sig_values[,1])
cols <- as.vector(sig_values[,2])

getInd <- function(trans){
  which(rownames(correlation) == trans)
}

hits <- data.frame(t1 = rownames(correlation.pvalue)[rows], t2 = colnames(correlation.pvalue)[cols], Correlation = correlation[sig_inds], p_value = correlation.pvalue[sig_inds])

hits.order <- hits[order(hits$p_value),]
hits.order <- hits.order[seq(2, 50, 2),]

cor.df <- as.data.frame(correlation)


```


```{r}
t.scal.auc.df <- as.data.frame(t(scal.auc.df))

scat <- ggplot(data = t.scal.auc.df, aes(y=ydjE, x=sapB)) + geom_point(size=3) + theme_bw()+ ylab("Normalized AUC - ∆ydjE") + xlab("Normalized AUC - ∆sapB") + geom_smooth(method=lm, se=FALSE, color ="grey") +theme(axis.title = element_text(size=18),
          axis.text = element_text(size=16),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          legend.position = "none",
          panel.border = element_rect(colour = "black", size = 2)) + xlim(-4.5, 2)+ ylim(-4.5, 2)



scat
```

```{r}

```

